---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tutorial.package

<!-- badges: start -->
<!-- badges: end -->

tutorial.package is a developmental package made for the Problem Set 3 of the UTexas Making Big Data course. This package has two major commands, AnalysisFunction and GetDataAsset, along with a pre-loaded dataset, PackageDataAsset.

## Installation

You can install the development version of tutorial.package like so:

``` {r}
library(devtools)
devtools::install_github("peterwdunphy/tutorial.package")
```

## AnalysisFunction

Function takes a a numeric array x and randomly adds white noise drawn i.i.d from unif(-1,1) to x when training = T. When training = F, the function simply returns x.

```{r example}
library(tutorial.package)
# Create a numeric array of length 10
x <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)

# Add random white noise to x during training
x_train <- AnalysisFunction(x, training = TRUE)

#  Check the result
print(x_train)
# Output: [1] 0.2671259 2.1374656 2.1014392 4.7121023 4.1662397 6.2558626 7.7542864 8.8569784 8.8682297 9.4225326

# Return the original x during inference
x_test <- AnalysisFunction(x, training = FALSE)

# Check the result
print(x_test)
# Output: [1] 1 2 3 4 5 6 7 8 9 10
```

## GetDataAsset

A function that has no inputs that will download the dataset stored in the Dropbox link. The function will download, unzip, and load the dataset into the R session, while removing the downloaded file from disk. Currently, the link contains the data used in the paper Robert Lalonde, "Evaluating the Econometric Evaluations of Training Programs," American Economic Review, Vol. 76, pp. 604-620. The data is also available by calling data(PackageDataAsset).


```{r cars}
data <- GetDataAsset()
# equivalently, data(PackageDataAsset)
```

## License

Creative Commons Attribution-Noncommercial-No Derivative Works 4.0, for academic use only.


